The transition redshift as a probe of reionization

### 2019-08-12 paper/ms.tex
Add more about intensity mapping, remove [OIII] references

\subsection{Intensity mapping} \label{ssec:oiii_int_map}
In order to model the relation between luminosity ($L$) and
halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
the mean luminosity of a halo of mass $M$ is,
\beq \label{eq:lum_mass_relation}
\avg{L}(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha}\text{,}
\eeq
where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
[\OIII] at that redshift and $\alpha$ is the power-law index. We then draw the
luminosity of each halo from a lognormal distribution of mean $\avg{L}(M)$ and
scatter $\sigma$. Once the average intensity is fixed (which we assume so),
this is a two-parameter model ($\alpha$ and $\sigma$) of the [\OIII]
luminosity-mass relation. In practice, the average intensity of the field only
enters in the detectability calculation, so we instead work in the convenient
units where $L_0=1$ and $M_0=10^{10}\,\Msun$.

\section{Results} \label{sec:results}
\subsection{The halo field}
We first investigate the dependence of the transition redshift as defined by
the halo field. Fig.~\ref{fig:ztran_vs_k} shows the transition redshift
defined by the 21~cm\,--\,density cross-power spectrum (see
Eq.~\ref{eq:ztran_def}) as a function of $k$. The three models considered in
this work are shown in orange, gray, and teal (\hot{}, \fid{}, and \cold{},
respectively).

>>>>

\subsection{Intensity mapping} \label{ssec:oiii_int_map}
In order to model the relation between luminosity ($L$) and
halo mass, we follow \citet{2019ApJ...874..133B}. Specifically, we assume that
the mean luminosity of a halo of mass $M$ is,
\beq \label{eq:lum_mass_relation}
\avg{L}(M) = L_0 \left[ \frac{M}{M_0} \right]^{\alpha}\text{,}
\eeq
where $L_0/M_0^{\alpha}$ is set to match the total average intensity of
the line at that redshift and $\alpha$ is the power-law index. We then draw the
luminosity of each halo from a lognormal distribution of mean $\avg{L}(M)$ and
scatter $\sigma$. Once the average intensity is fixed (which we assume so),
this is a two-parameter model ($\alpha$ and $\sigma$) of the
luminosity-mass relation. In practice, the average intensity of the field only
enters in the detectability calculation, so we instead work in the convenient
units where $L_0=1$ and $M_0=10^{10}\,\Msun$.

We assign a luminosity to each halo according to this prescription. An
important consideration is that we have not specified which line we are
working with. In detail, the relationship between a halo and it's luminosity
is a complicated function of the state of the interstellar medium of the
hosted galaxy, which can depend upon a number of both deterministic and
stochastic quantities. Our model crudely attempts to account for this by
including some random scatter, but will ultimately be a rough description of
reality.

{\bf Some words justifying why our simple model will extend to more
complicated luminosity-halo relations.}

\section{Results} \label{sec:results}
\subsection{The halo field}
{\bf If we switch to LIM I think this section should be scrapped, except
showing ztran vs k but using LIM and density instead of halos}

We first investigate the dependence of the transition redshift as defined by
the halo field. Fig.~\ref{fig:ztran_vs_k} shows the transition redshift
defined by the 21~cm\,--\,density cross-power spectrum (see
Eq.~\ref{eq:ztran_def}) as a function of $k$. The three models considered in
this work are shown in orange, gray, and teal (\hot{}, \fid{}, and \cold{},
respectively).
